Landscape composition and beneficial insects

### 2020-05-29 manuscript/manuscript_outline.Rmd
Updated figures and wrote some more in the Intro

bibliography: refs.bib
# csl: ecology-letters.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    toc: false
    fig_caption: false
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

@@

#Load models
load('../data/PteMelMod.Rdata')
load('../data/ParDisMod.Rdata')
load('../data/OpilioMod.Rdata')

@@

@@

@@

* We don't have a good understanding of what drives beneficial arthropod abundance
  + Bees are generally driven by flower/nest substrate availability [@roulston2011]
  + Limited understanding of other arthropods
  + Beetles are limited by water, food, and oviposition sites [@lovei1996]
  + Arachnids are similarly limited by food, shelter

* Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
  + No-till agriculture is better for some ground beetles [@busch_Msc]
  + How can we design landscapes to benefit both farmers and insects?

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
  + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
  + We hypothesized that:
  1. Abundance of semi-natural land (SNL) would result in increased arthropod abundance
  2. Nearby SNL acts as a source of arthropods earlier in the season, and act as a sink later on, as arthropods migrate into margins to reproduce

@@

* Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989; @ramsay2003]
  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
  + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)

@@

## _Pterostichus melanarius_

* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelCoefs-linTerms), \@ref(tab:PteMelCoefs-smoothTerms))
  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelCoefs-fixeff)a)
  + This indicates that low-density stands of canola may allow faster movement of ground beetles.
  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelCoefs-fixeff)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelCoefs-fixeff)d)
  + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season

```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
pmelLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',
      col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}

pmelSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
      col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
      digits=c(1,2,2,2),align='rrll',escape=TRUE)
```

```{r PteMelCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-fixeff} Landscape influence on _Pterostichus melanarius_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pterostichus_melanarius_fixeff.png')
```

*  _P. melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelCoefs-raneff))
  + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field

```{r PteMelCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-raneff} Temporal and spatial components of _Pterostichus melanarius_ activity density'}
  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
```

## _Pardosa distincta_

* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisCoefs-linTerms), \@ref(tab:ParDisCoefs-smoothTerms)), similar to _P. melanarius_.
  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisCoefs-fixeff)a).
  + Interestingly, nearby canola appeared to act as a source of _P. distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,pTable[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Canola'])`)
  + Pulse crops had a similar effect, acting as a source of _P. distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
  + Similar to _P. melanarius_, _P. distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,pTable[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))

```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll',escape=TRUE)
```

```{r ParDisCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-fixeff} Landscape influence on _Pardosa distincta_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_distincta_fixeff.png')
```

```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-raneff} Temporal and spatial components of _Pardosa distincta_ activity density'}
  include_graphics('../figures/Pardosa_distincta_raneff.png')
```

## _Pardosa moesta_

```{r ParMoeCoefs-linTerms, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='\\label{tab:ParMoeCoefs-linTerms} Linear terms for _Pardosa moesta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r ParMoeCoefs-smoothTerms, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='\\label{tab:ParMoeCoefs-smoothTerms} Smooth terms for _Pardosa moesta_. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll')
```

```{r ParMoeCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-fixeff} Landscape influence on _Pardosa moesta_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_moesta_fixeff.png')
```

```{r ParMoeCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-raneff} Temporal and spatial components of _Pardosa moesta_ activity density'}
  include_graphics('../figures/Pardosa_moesta_raneff.png')
```

## _Phalangium opilio_

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, pTable[loc=='Pivot'])`, `r with(opilLinTerms, pTable[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,pTable[grepl('E,N',Smoother)])`, and Easting

```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
opilLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
opilSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for \\emph{Phalangium opilio}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. df_','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll')
```

```{r OpilioCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-fixeff} Landscape influence on _Phalangium opilio_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence regions. Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Opiliones_fixeff.png')
```

```{r OpilioCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-raneff} Temporal and spatial components of _Phalangium opilio_ activity density'}
  include_graphics('../figures/Opiliones_raneff.png')
```

@@

* Pterostichus responded to landscape composition

\newpage

@@

```{r concurvity, echo=FALSE, fig.cap='\\label{fig:concurvity} Concurvity estimates for top land cover classes'}  
  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
```

>>>>

bibliography: refs.bib
# csl: ecology-letters.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    toc: false
    fig_caption: true
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

@@

#Load models
load('../data/PteMelMod.Rdata')
load('../data/ParDisMod.Rdata')
load('../data/ParMoeMod.Rdata')
load('../data/OpilioMod.Rdata')

@@

#Extract Pardosa moesta results
pmoeRes <- summary(ParMoeMod$mod3)
pmoeLinTerms <- pmoeRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
pmoeSmTerms <- pmoeRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold

@@

# #Extract concurvity from PteMel model
# mod3concurv <- concurvity(PteMelMod$mod3,FALSE)$estimate

@@

* Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
  + Bees are generally driven by flower/nest substrate availability [@roulston2011]
  + Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
  + Beetles are limited by water, food, and oviposition sites [@lovei1996]
  + No-till agriculture is better for some ground beetles [@busch_Msc]
  + Arachnids are similarly limited by food, shelter

* Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
  + Spillover occurs when organisms migrate from suitable habitat patches
  + Can occur with pests or beneficial organisms [@woodcock2016]
  + Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
  + This means that spillover depends not only on habitat type, but on time of the year
  + Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
  + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]

* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
  + We hypothesized that:
  1. Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods, depending on habitat preferences
  2. Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods. However, pest phenology/crop senescence at the end of the season causes a decrease in the number of pests. This means that crop cover may act as a sink for beneficial insects early in the season as they migrate into the crop, and a source later on as they migrate out of the crop

@@

* Functional regression plots of landscape composition may seem cryptic, but are fairly straightforward to interpret:
  + Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. organisms spill over *from* it)
  + Neutral responses indicate that the cover class does not act as a significant source or sink
  + However, negative responses to nearby landscape cover classes indicate one of two things
  + 1) It indicates that the cover class acts as a sink (i.e. organisms spill over *into* it)
  + 2) It indicates that the cover class acts as a source, but is unoccupied (i.e. no organisms available to spill over)
  +

* Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989; @ramsay2003]
  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
  + Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63)
  + Forest and shrubland were combined into the ``TreeShrub" category, grassland and wetland were combined into the "GrassWetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
  + Cereal was removed from the model, as it was negatively correlated with canola at distances less than 200m and positively correlated at distances over 500m, likely reflecting the most common crop rotations and landscape structure present across our study region

@@

## Pterostichus melanarius

* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth))
  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelLandscape)a) 
  + This indicates that low-density stands of canola may allow faster movement of ground beetles.
  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelLandscape)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelLandscape)d)
  + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season

```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pterostichus_melanarius_fixeff.png')
```

*  _P. melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
  + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field

```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
```

## Pardosa distincta

* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), similar to _P. melanarius_.
  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a).
  + Interestingly, nearby canola appeared to act as a source of _P. distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Canola'])`)
  + Pulse crops had a similar effect, acting as a source of _P. distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,p[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisLandscape)d)
  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
  + Similar to _P. melanarius_, _P. distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,p[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))

```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_distincta_fixeff.png')
```

```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
  include_graphics('../figures/Pardosa_distincta_raneff.png')
```

## Pardosa moesta

* _P. moesta_ was also heavily influenced by trap location and landscape composition (Tables \@ref(tab:ParMoeLinear), \@ref(tab:ParMoeSmooth))
  + Similar to the other Lycosid spider _P. distincta_, _P. moesta_ had much lower activity density in canola than any other trap location (Figure \@ref(fig:ParMoeLandscape)a)
  + Nearby canola also acted as a source of _P. moesta_ (Figure \@ref(fig:ParMoeLandscape)b, p = `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`), although the effect was only strong at the end of the season (p = `r with(pmoeSmTerms,p[Smoother=='ti(distMat,endDayMat):Canola'])`)
  + This indicates that both _P. distincta_ and _P. moesta_ migrate out of canola into adjacent habitat in order to overwinter or oviposit
  + _P. moesta_ also had similar responses to pulses (Figures \@ref(fig:ParMoeLandscape)d)
  + _P. moesta_ responded negatively to nearby tree and shrub cover, indicating that they are possible sinks of 
  + Urban land cover was a sink, but only at certain times of the year

```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on \\emph{Pardosa moesta} activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_moesta_fixeff.png')
```

```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
  include_graphics('../figures/Pardosa_moesta_raneff.png')
```

## Phalangium opilio

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + This indicates that _P. opilio_ activity density is shaped mostly by large-scale geographic patterns, rather than landscape composition

```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence regions. Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Opiliones_fixeff.png')
```

```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
  include_graphics('../figures/Opiliones_raneff.png')
```

@@

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition

* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition

* The harvestman _Phalangium opilio_ did not respond to landscape composition

* 
\newpage

@@

```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for top land cover classes'}  
  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
```

```{r PteMelLinear, echo=FALSE, warning=FALSE}
pmelLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r PteMelSmooth, echo=FALSE, warning=FALSE}
pmelSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
      col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
      digits=c(1,2,2,2),align='rrll',escape=FALSE)
```

```{r ParDisLinear, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Pardosa distincta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r ParDisSmooth, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll',escape=FALSE)
```

```{r ParMoeLinear, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Pardosa moesta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r ParMoeSmooth, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pardosa moesta}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll',escape=FALSE)
```

```{r OpilioLinear, echo=FALSE, warning=FALSE}
opilLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r OpilioSmooth, echo=FALSE, warning=FALSE}
opilSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Phalangium opilio}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll',escape=FALSE)
```
